The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals

### 2021-01-22 publications/2020-03-paper/highlights/highlights.tex
chapman corrections
Former-commit-id: 34ff7f9fee444823f431591fdb1c5c7bc67cbaa8
Former-commit-id: 2a9e415a4bda7c1d79adfd494a80e1a73e133505

\begin{document}
\begin{frontmatter}
\title{The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
	\item Transition pathways using nuclear, renewables, carbon capture, and hydrogen.
	\item Includes long-term assessment up to 2100 
	\item Dynamic simulations use learning curves for cost and emissions..
	\item Sensitivity analysis identifies key parameters and thresholds.
\end{itemize}
\end{document}

>>>>

\begin{document}
\begin{frontmatter}
\title{The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
	\item Identifies potential transition pathways for Japan using multiple technologies.
	\item Simulations to the year 2100 identify post-2050 impacts of a stabilizing transition. 
	\item Dynamic simulations use learning curves for cost and emissions.
	\item Sensitivity analysis identifies key parameters, thresholds, and trade-offs.
\end{itemize}
\end{document}
